---
title: "P8105 Homework 1 [td2704]"
output: github_document
---


```{r, echo=FALSE, message=FALSE}

library(tidyverse)

```

## Problem 1

```{r}

df = tibble(
  vec_randsample = rnorm(10),
  vec_logical = vec_randsample > 0,
  vec_char = c("zero", "one", "2", "3", "this", "is", "a", "character", "vector", "9"),
  vec_factor = factor(c("agree", "disagree", "agree", "neutral", "disagree", "agree", "agree", "neutral", "disagree", "neutral"))
)

df

```
Trying to take mean of each variable in df:

```{r}

mean(pull(df,vec_randsample))
mean(pull(df,vec_logical))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))

```

Taking the mean of the random sample and logical vector work, but the character
and factor vector means don't work.

```{r, echo=TRUE, results='hide'}

as.numeric(pull(df,vec_logical))
as.numeric(pull(df,vec_char))
as.numeric(pull(df,vec_factor))

mean(as.numeric(pull(df,vec_logical)))
mean(as.numeric(pull(df,vec_char)))
mean(as.numeric(pull(df,vec_factor)))

```

As we can see above, the logical and factor variables were converted to
numeric values, while the character variable is unable to be converted since
there aren't numeric equivalences. Logical variables convert to 1s and 0s for
Trues and Falses, while factor variables convert to numbers representing the
three different 'levels'. R automatically sees logical variables as 1s and 0s,
which is why 'mean' worked on it initially. After converting the factor
variable to numeric, 'mean' works on it now as well, although the 
interpretation of that mean may not be useful. We are unable to take the mean
of character variables or convert them to numeric values if there is no
equivalence to an actual numeric value (some of the chars like "2" were able
to convert to numeric 2). 


